\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-28 paper/experiments.tex

\begin{figure}
\includegraphics[width=\columnwidth]{figures/running_times_combined.png}
\caption{Query runtimes with imputation on base tables, \ProjectName{}
    optimizing for quality ($\alpha=0$), and \ProjectName{} optimizing for
    performance ($\alpha=1$). Quality-optimized, on-the-fly imputation provides an order of
    magnitude speedup over imputing on base tables. Efficiency-optimized on-the-fly
    imputation can provide another order-of-magnitude speedup at the expense of quality. For
    relatively expensive queries over large datasets (Query 9), runtime of imputation can be reduced from \acsbaseresulthours~to \acsimputedbzeroresult. }
\label{fig:runtimes}
\end{figure}

@@

In many real-world cases, applying the imputation step at the base table is prohibitively
expensive.
To illustrate the increasing difficulty of such an approach as datasets scale, we run~\Cref{q9} over the ACS dataset.
Applying the imputation operation to the base table is extremely expensive, in our case
completing in \acsbaseresultminutes (\Cref{fig:runtimes}. In contrast, \ProjectName{} executes a quality-optimized version
in\acsimputedbzeroresult~and a runtime-optimized version in \acsimputedboneresult. This highlights the potential
benefit of using our system for early data exploration.

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{figures/running_times_combined.png}
\caption{Query runtimes with imputation on base tables, \ProjectName{}
    optimizing for quality ($\alpha=0$), and \ProjectName{} optimizing for
    performance ($\alpha=1$). Quality-optimized, on-the-fly imputation provides an order of
    magnitude speedup over imputing on base tables. Efficiency-optimized on-the-fly
    imputation can provide another order-of-magnitude speedup at the expense of quality. For
    relatively expensive queries over large datasets (Query 9), runtime of imputation can be reduced from \acsbaseresulthours~to \acsimputedbzeroresult. \srm{make this a bar graph}}

\label{fig:runtimes}
\end{figure}

@@

\subsubsection{Runtime of Base-table Imputation}
In many real-world cases, applying the imputation step at the base table is prohibitively
expensive.
To illustrate the increasing difficulty of such an approach as datasets scale, we run~\Cref{q9} over the ACS dataset.
Applying the imputation operation to the base table is extremely expensive, in our case
completing in \acsbaseresultminutes (\Cref{fig:runtimes}. In contrast, \ProjectName{} executes a quality-optimized version
in\acsimputedbzeroresult~and a runtime-optimized version in \acsimputedboneresult. This highlights the potential
benefit of using our system for early data exploration.

\srm{note somewhere that imputation requires both training and running model, and state why this is reasonable / the only choice}
